---
title: "P8105 Homework 1"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

## Problem 1: 

### Loading the penguin dataset 
```{r}
data("penguins", package = "palmerpenguins")
```

### Description of the penguins dataset 
The 'penguins' dataset contains data about different penguin species. It contains data on `r nrow(penguins)` penguins, with `r ncol(penguins)` variables that provide measurements and characteristics of penguins. The dataset includes the variables
**species** (the type of penguin (Adelie, Chinstrap, or Gentoo)),
**island** (the island where the penguins were observed (Torgersen, Biscoe, or Dream)),
**bill_length_mm** (the length of the penguin's bill in millimeters),
**bill_depth_mm** (the depth of the penguin's bill in millimeters),
**flipper_length_mm** (the length of the penguin's flippers in millimeters),
**body_mass_g** (the penguin's body mass in grams),
**sex** (the sex of the penguin (male or female)), and
**year** (the year in which the penguins were observed).

The dataset has a total of `r nrow(penguins)` rows and `r ncol(penguins)` columns. The mean flipper length of the penguins is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)`mm.


### Making a Scatterplot 

```{r yx_scatter}
ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
  geom_point()
ggsave("flipper_vs_bill_scatterplot.png", width = 6, height = 4)
```


## Problem 2: 
